### 2014-02-18 thesis/src/chapters/chapter-design.tex
Thesis: spellings

\section{Motivation}
As one can see, latest advances in providing platform-as-a-service still do not yield a comprehensive solution that embraces a range of fine-grained actions relevant to a given situation in an environment, as it was summarised in previous chapter. All of the presented solutions solely engage horizontal scaling, while other IT processes and corresponding actions such as vertical scaling, cloud bursting or application platform restart remains neglected. What is more, none of the investigated systems takes proactive approach in enforcing given QoS. To make matter worse, some platforms such as Carina or OneFlow are provider-specific, hence, requiring vast knowledge and time of entities responsible for its supervision.

What system has all of the above-mentioned features is self-adaptive one. As \cite{brun2009engineering} advocates, one of the first architectures of a self-adaptive system was presented in IBM's blueprint for autonomic computing \cite{IBM06}. Since IBM's autonomic system is widely recognised and respected model, we decided to leverage it as a foundation of our work. A concept of autonomic system is alluring due to its four crucial attributes:
\begin{itemize}
 \item \emph{self-configuration} - dynamic adaptation to changing environment such as provisioning new application instances, application tuning, traffic delegation to an external provider
  \item \emph{self-healing} - discovering, diagnosing and reacting to environment disruption such as container outage
  \item \emph{self-optimising} - monitoring and tuning resources: migrating containers, offloading traffic, for example
  \item \emph{self-protecting} - detecting and protecting against threats such as Deny-of-Service by provisioning extra resources
\end{itemize}

>>>>

\section{Motivation}
As one can see, latest advances in providing platform-as-a-service still do not yield a comprehensive solution that embraces a range of fine-grained actions relevant to a given situation in an environment, as it was summarised in previous chapter. All of the presented solutions solely engage horizontal scaling, while other IT processes and corresponding actions such as vertical scaling, cloud bursting or application platform restart remains neglected. What is more, none of the investigated systems take proactive approach in enforcing given QoS.

What has all of the above-mentioned features is a self-adaptive system that has a holistic approach to application scaling. As \cite{brun2009engineering} advocates, one of the first architectures of a self-adaptive system was presented in IBM's blueprint for autonomic computing \cite{IBM06}. Since IBM's autonomic system is widely recognised and respected model, we decided to leverage it as a foundation of our work. A concept of autonomic system is alluring due to its four crucial attributes:
\begin{itemize}
 \item \emph{self-configuration} - dynamic adaptation to changing environment such as provisioning new application instances, application tuning, traffic delegation to an external provider
  \item \emph{self-healing} - discovering, diagnosing and reacting to environment disruption such as container outage
  \item \emph{self-optimising} - monitoring and tuning resources: migrating containers, offloading traffic, for example
  \item \emph{self-protecting} - detecting and protecting against threats such as Deny-of-Service by provisioning extra resources
\end{itemize}
